HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-10-19 scnn.tex
updated info about the dataset

\begin{figure}
\includegraphics[width=\linewidth]{figure_example_maps}
\caption{Example maps on the sphere:
(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
These maps were pixelised using $N_{side} = 512$.
The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
}
\label{fig:example_maps}
\end{figure}

@@

The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
The classification methods were trained to predict a label from a HEALPix map.
Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online. Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.

>>>>

\begin{figure*}
\includegraphics[width=\linewidth]{figure_example_maps}
\caption{Example maps on the sphere:
(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
These maps were pixelised using $N_{side} = 512$.
The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
}
\label{fig:example_maps}
\end{figure*}

@@

The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
The classification methods were trained to predict a label from a HEALPix map.
% Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online. Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.
Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} to reproduce those experiments are openly available online.
The data is available upon request from the cosmology group\footnote{\url{www.cosmology.ethz.ch}}.
Furthermore, Jupyter notebooks demos can be run from your browser without installing anything.
